### 2023-09-14 3.Design/crossbar.tex
Symbol is finished

%TODO understand better \subsection{Sneak path problem}
\subsection{Symbol}
This is the symbol defined for the voltage based memristor crossbar array used in this thesis for a better undertsanding of the future circuits. It depends on several parameters, the number of inputs ($n_i$), the number of outputs ($n_o$) and the serial size ($n_s$).

%TODO : include figure

>>>>

%TODO understand better \subsection{Sneak path problem}
\subsection{Symbol}
The symbol (\cref{sym:xbar}) defined for the voltage based memristor crossbar array used in this thesis is more compact and helps the readability of the final circuit. It depends on several parameters, the number of inputs ($n_i$), the number of outputs ($n_o$) and the serial size ($n_s$).

\begin{figure}[H]
  \centering
  \includesvg[height=2.5cm]{crossbar/xbarSymbol}
  \caption{Symbol used for the crossbar array}
  \label{symb:xbar}
\end{figure}
